RDF Validation of Metadata \\ on Person-Level and Aggregated Data

### 2015-03-03 paper/paper7/paper7.tex
4.2

\textbf{Frequencies and Descriptive Statistics.}
Restricting data property ranges [$V_{min}$,$V_{max}$] within the context of given classes is a very common requirement (\emph{R-45: literal ranges}) 
- disco:CategoryStatistics resources, e.g., point to percentage values via the data property \emph{disco:percentage}; 
these values must be of the datatype \emph{xsd:double} and must be between 0 and 100.

>>>>

\textbf{Frequencies and Descriptive Statistics.}
Percentage values are valid when they are between 0 and 100.
The constraint type \emph{literal ranges} (\emph{R-45}) restricts data property ranges [$V_{min}$,$V_{max}$] within the context of given classes.
A constraint of this type applies to the property \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set ($\mathcal{SL}_{2}$).
